\papertitle

### 2021-03-10 source_separation/paper/paper.tex
add references for NMF
fix accent in institutions

%%Affiliations
\affil[1]{\department{Center for New Music and Audio Technologies}\institution{University of California, Berkeley}\city{Berkeley}\state{California}\country{USA}\affiliationtype{University}}
\affil[2]{\department{\'Ecole Normale Sup\'erieure Paris-Saclay}\institution{Universi\'e Paris-Saclay}\city{Paris}\state{}\country{France}\affiliationtype{University}}
\affil[3]{\department{Laboratoire des Signaux et Syst\`emes}\institution{Centrale Supélec, CNRS, Université Paris-Saclay}\city{Paris}\state{}\country{France}\affiliationtype{University}}

@@

			\subsubsection{Non-negative Matrix Factorization}
			@Max

>>>>

%%Affiliations
\affil[1]{\department{Center for New Music and Audio Technologies}\institution{University of California, Berkeley}\city{Berkeley}\state{California}\country{USA}\affiliationtype{University}}
\affil[2]{\department{\'Ecole Normale Sup\'erieure Paris-Saclay}\institution{Universi\'e Paris-Saclay}\city{Paris}\state{}\country{France}\affiliationtype{University}}
\affil[3]{\department{Laboratoire des Signaux et Syst\`emes}\institution{Centrale Sup\'elec, CNRS, Universit\'e Paris-Saclay}\city{Paris}\state{}\country{France}\affiliationtype{University}}

@@

			\subsubsection{Non-negative Matrix Factorization}
			@Max 
			We use scikit learn implementation. Related papers:
			\cite{Cichocki_NMF} \cite{Fevotte_NMF}
